### 2017-04-18 CS798-ConvexityAndOptimization/assignments/assignment_03.tex
wroteup 3

&\geq exp(\frac{1}{8(n-1)}).

@@

$$vol(\cE_{t+1}) \leq exp(\frac{-1}{n}) vol(\cE_t).$$

@@

$$vol(\cE_t) \leq exp(\frac{-1}{n})^t vol(RB^n_2).

@@

$$vol(rB^n_2) \leq exp(\frac{-1}{n})^t vol(RB^n_2)$$

@@

%Question 3
\section{}
\end{document}

>>>>

&\geq \exp(\frac{1}{8(n-1)}).

@@

$$vol(\cE_{t+1}) \leq \exp(\frac{-1}{n}) vol(\cE_t).$$

@@

$$vol(\cE_t) \leq \exp(\frac{-1}{n})^t vol(RB^n_2).

@@

$$vol(rB^n_2) \leq \exp(\frac{-1}{n})^t vol(RB^n_2)$$

@@

%Question 3
\section{}
\paragraph{}
Let $f(x) = \exp(-h(x))$ where $h$ is a differentiable function.
\subsection{a}
\paragraph{}
We want to show $f$ is log-concave (ie. $h$ is convex) if and only if $f''(x)f(x) \leq (f'(x))^2$. We compute the first and second derivatives of $f$. The first derivative is
$$f'(x) = \exp(-h(x))\cdot (-h'(x)).$$
The second derivative is 
$$f''(x) = \exp(-h(x)) \cdot (h'(x))^2 + \exp(-h(x))(-h''(x)) = \exp(-h(x))((h'(x))^2 - h''(x)).$$
So the left hand side is
$$f''(x)f(x) = \exp(-h(x))^2((h'(x))^2 - h''(x))$$
and the right hand side is
$$(f'(x))^2 = \exp(-h(x))^2(h'(x))^2.$$
So we have have $f''(x)f(x) \leq (f'(x))^2$ if and only if $h''(x) \geq 0$ for all $x$. But this second order condition is satisfied if and only if $h$ is convex, and therefore $f$ is log-concave.$\blacksquare$
\subsection{b}
\paragraph{}
Suppose $h$ is convex. Let $F(x) = \int_{-\infty}^x f(y) dy$. Let $x \in \R$ and suppose that $h'(x) < 0$. From the fundamental theorem of calculus, $F'(x) = f(x)$. Now let 
$$I(x) = -h'(x)F(x)$$.
Then $$I'(x) = -h''(x)F(x) -h'(x)F'(x) \leq -h'(x)f(x)$$
since $h''(x) \geq 0$ as $h$ is convex. Taking antidervatives we see
$$I(x) \leq f(x).$$
Thus
$$F(x) \leq \frac{f(x)}{-h'(x)}$$
since $h'(x) < 0$. So we have
$$\int_{-\infty}^xf(y)dy \leq \frac{\exp(-h(x))}{-h'(x)}$$
as desired. $\blacksquare$
\paragraph{}
Now we show that $F$ is log-concave. We have
$$F'(x) = f(x)$$
and
$$F''(x) = -h'(x)f(x).$$
Therefore
$$F''(x)F(x) = -h'(x)f(x) F(x)$$
and
$$(F'(x))^2 = f(x)^2.$$
If $h'(x) \geq 0$ then 
$$F''(x) F(x) \leq 0$$
and so $F''(x)F(x) \leq (F'(x))^2$ immediately. Now if $h'(x) < 0$ then we use the inequality we just demonstrated, so
$$F''(x) F(x) = -h'(x)f(x)F(x) \leq -h'(x)f(x) \cdot \frac{f(x)}{-h'(x)} = f(x)^2.$$
Therefore by part $3a$, $F(x)$ is log-concave. $\blacksquare$
\end{document}
